---
title: "p8105_hw6_tt2714"
author: "Tiffany Tu"
date: "11/19/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(tidyverse)
library(knitr)
library(MASS)
library(forcats)
library(broom)
library(modelr)
library(ggplot2)
```

## Problem 1
#### Data cleaning...
A city_state variable is created to combine the two columns city and state. Four cities that do not report victim race are removed. Disposition, victim_race, and victim_sex columns are coded into binary variables.      
```{r message = FALSE, warning = FALSE}
homicide = read_csv(file = "./homicide-data.csv") 
homicide_citystate = homicide %>% 
  unite(city_state, c(city, state), sep = ", ", remove = T) %>% 
  filter(!grepl('Dallas|Phoenix|Kansas City|Tulsa', city_state)) %>% 
  mutate(disposition = ifelse(disposition == "Closed by arrest", 1, 0),
         victim_race = ifelse(victim_race == "White", "white", "non-white")) %>% 
  mutate(victim_age = as.numeric(victim_age), 
         victim_sex = as.factor(victim_sex),
         victim_race = fct_relevel(victim_race, "white")) 
```

#### Logistic Regression Model for Baltimore, MD 
Outcome: disposition of homicide    
Reference group: race - white        
Predictors: sex and age    

Use `broom::tidy` to clean up the model and include odds ratio with confidence intervals. 
```{r}
baltimore = homicide_citystate %>% filter(city_state == "Baltimore, MD")
baltimore_glm = glm(disposition ~ victim_race + victim_age + victim_sex, 
                    data = baltimore, family = binomial())

baltimore_glm %>% 
  broom::tidy(., conf.int = TRUE) %>% 
  mutate(odds.ratio = exp(estimate),
         conf.low = exp(conf.low),
         conf.high = exp(conf.high)) %>% 
  kable(digits = 3)
```

#### Regression on all cities
Logistic regression on all cities with odds ratio and confidence intervals.
```{r}
cities_glm = homicide_citystate %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(models = map(data, ~glm(disposition ~ victim_race + victim_age + victim_sex, data = .x)),
         models = map(models, broom::tidy)) %>% 
  dplyr::select(-data) %>% 
  unnest() %>% 
  mutate(odds.ratio = exp(estimate),
         conf.low = exp(estimate - std.error * 1.96),
         conf.high = exp(estimate + std.error * 1.96)) %>% 
  filter(term == "victim_racenon-white")
```

```{r}
cities_glm %>% ggplot(aes(color = reorder(city_state, odds.ratio))) +
  geom_point(aes(x = reorder(city_state, odds.ratio), y = odds.ratio)) +
  geom_errorbar(aes(x = city_state, ymin = conf.low, ymax = conf.high)) +
  coord_flip() + ggtitle("Adjusted odds ratio of non-white to white in each city") +
  xlab("city") + ylab("adjusted odds ratio") + 
  theme(axis.text.y = element_text(size = 6), legend.position = "none") 
```
* comment on plot   

## Problem 2
```{r message = FALSE, warning = FALSE}
birthweight = read_csv(file = "./birthweight.csv")
birthweight_new = birthweight %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform))
```
This dataset consists of `r ncol(birthweight)` variables on a child's birthweight. There is a total of `r nrow(birthweight)` entries of children data. The data is prepared for regression analysis with appropriate format and no missing data. 

#### Regression Model for Birthweight
I am using a step-wise regression (backward direction) for variable selection, as we have `r ncol(birthweight_new) - 1` variables available for birthweight prediction. 
```{r results = FALSE}
model_1 = lm(bwt ~ ., data = birthweight_new)
stepwise_1 = step(model_1, direction = 'backward') %>% 
  broom::tidy()
```

```{r}
stepwise_1 %>% kable()
```

This results in `r nrow(stepwise_1) - 1` correlated predictors for birthweight. But because this is still a lot of predictors to be considered, I select the top four with highest coefficients for my model: `babysex`, `blength`, `parity`, and `bhead`.

```{r}
model_1regression = lm(bwt ~ babysex + blength + parity + bhead, data = birthweight_new )
```

From the plot we see a heavy cluster from weight 2500 to 3500 around the zero mark for residual. However, there remains several outliers below the weight of 1500. 
```{r}
model_1graph = birthweight_new %>% 
  add_predictions(., model_1regression) %>% 
  add_residuals(., model_1regression) 

model_1graph %>% 
  ggplot(., aes(x = pred, y = resid)) +
  geom_point(alpha = 0.15) +
  xlab("Predicted Values") + ylab("Residuals") + 
  ggtitle("Residual against fitted values for birthweight prediction")
```

#### Additional Models
Predictors: length at birth and gestational age
```{r}

```

Head circumference, length, sex and all
```{r}

```

#### Comparing Models
Comparing my model with cross-validation prediction error